Selective Sequential Model Selection

### 2015-11-10 paper.tex
one more comment on sampling group LASSO conditional on directions

I also understand your argument that for $\ell_1$  the next entry test is less bad than I thought. 
To check the KKT conditions at $\hat{\theta}^{\lambda}(Y)$ for $\ell_1$ is 
straightforward, as $\hat{\theta}^{\lambda}(Y^*)$ has 
an explicit candidate form so we have a very good guess
at what the residuals at slightly later $\lambda$'s should look like and we
can check the KKT conditions easily.
For group LASSO, things are more complicated
as we probably will not want to condition on the ``signs'' which are now
a collection of unit vectors. If we don't condition on them
then we have to solve group LASSO for response $Y^*$ until the set of
active groups changes.
Even if we do condition on them (which is OK
as they are measurable with respect the right $\sigma$-algebra) the simplification for sampling that we observe for $\ell_1$ goes away. After $k$ steps on the
discrete $\Lambda$ path I think we are back to having 
$O(p*k)$ constraints roughly for any penalty that is not $\ell_1$. (For group
LASSO, the $O(p*k)$ estimate assumes $k$ is not huge, and each group has roughly bounded number of features in it.)}

>>>>

I also understand your argument that for $\ell_1$  the next entry test is less bad than I thought. 
To check the KKT conditions at $\hat{\theta}^{\lambda}(Y)$ for $\ell_1$ is 
straightforward, as $\hat{\theta}^{\lambda}(Y^*)$ has 
an explicit candidate form so we have a very good guess
at what the residuals at slightly later $\lambda$'s should look like and we
can check the KKT conditions easily.
For group LASSO, things are more complicated
as we probably will not want to condition on the ``signs'' which are now
a collection of unit vectors. If we don't condition on them
then we have to solve group LASSO for response $Y^*$ until the set of
active groups changes.
Even if we do condition on them (which is OK
as they are measurable with respect the right $\sigma$-algebra) the simplification for sampling that we observe for $\ell_1$ goes away. After $k$ steps on the
discrete $\Lambda$ path I think we are back to having 
$O(p*k)$ constraints roughly for any penalty that is not $\ell_1$. (For group
LASSO, the $O(p*k)$ estimate assumes $k$ is not huge, and each group has roughly bounded number of features in it.) Finally, conditioning on the
direction vectors needs a sampling algorithm that is not as simple as
Gaussian subject to affine constraints. Describing this sampler is something
I think we just don't want to touch in this paper.
}
